Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/approach.tex
minor modification

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

>>>>

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

### 2014-07-30 sections/discussion.tex
minor modification

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
\pick{This topic of discuss should be changed....}
 % noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

>>>>

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
\pick{This topic of discuss should be changed....}
 % noisy data, and binary classification

Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores. The classification of useless comments also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. As the manual classification can be subjective, these comments were not received three voting scores.  It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.

Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

### 2014-07-30 sections/results.tex
minor modification

%%Interpret: comments & model%%%%
As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area. Similarly, most comments in the red area are useless. The unclear comments are drawn in both area. Between these areas, there is an overlap section. This is because the similarity and dissimilarity values between useful and useless are vague. Both models tend to maximize coverage of classification. Thus, it is possible that there is overlap between these two models. However, from the results in Table \ref{tb:classify_number}, only three comments were classified overlap section. This shows that error of our models is low. Furthermore, there are 12 useless comments  (14\%) and  21 useful comments (17\%) still are undetermined (drawn in white area). We investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

\begin{table}[!t]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 \\
Useless & 69 & 23 & 7 & 6 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores. The classification of useless comments also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. As the manual classification can be subjective, these comments were not received three voting scores.  It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.

>>>>

%%Interpret: comments & model%%%%
As shown in the figure, most comments drawn in green area are useful labels and very few useless labeled comments drawn in this area. Similarly, most comments in the red area are useless labels. The unclear comments are drawn in both area. Between these areas, there is an overlap section. This is because the similarity and dissimilarity values between useful and useless are vague. Both models tend to maximize coverage of classification. Thus, it is possible that there is overlap between these two models. However, from the results in Table \ref{tb:classify_number}, only three comments were classified overlap section. This shows that error of our models is low. Furthermore, there are 12 useless comments  (14\%) and  21 useful comments (17\%) still are undetermined (drawn in white area). We investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

\begin{table}[!t]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
Result from & \multicolumn{4}{c}{Label set by manual assessment} \\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 \\
Useless & 69 & 23 & 7 & 6 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

@@
